Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-11 R0V0.tex
Add a comment on integrability

An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered. The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below). This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

>>>>

An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered. The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed solution (see a precise definition below). In contrast to feedback linearization which depends on integrability, the obtained controller depends only on the stabilizability property of the system. This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.
